\section{Trace}

Ah...we're finally dealing with concrete matrices and numbers.
This is stuff you should be familiar with from Linear Algebra I.

\begin{definition}
  Suppose $T \in \L(V)$.
  \begin{itemize}
    \item If $\F = \C$, then the \textbf{trace} of $T$ is the sum of eigenvalues of $T$, with each eigenvalue repeated according to its multiplicity.
    \item If $\F = \R$, then the \textbf{trace} of $T$ is the sum of eigenvalues of $T_{\C}$, with each eigenvalue repeated according to its multiplicity.
  \end{itemize}
  The trace of $T$ is denoted $\vtrace T$.

  We also later see that the \textbf{trace} of a square matrix $A$, denoted $\vtrace A$, is defined to be the sum of the diagonal entries of $A$.
\end{definition}

\bx{
  Not sure how the author wants this to be proved, but every $T$ has a corresponding matrix $\mathcal{M}$, so if $T$ is invertible, then its matrix for the inverse must exist as well.
}

\bx{
  Inverses are unique so we know $B = A^{-1}$.
}

\bx{
  This means for the matrix $\M$ of $T$, we have
  \begin{equation*}
    \M = A^{-1}\M A
  \end{equation*}
  for any change of basis. This isn't formal, but only $\M = I$ satisfies this equation it seems $\forall A$.
}

\bx{
  $T$ acts like the identity. We have to formalize this, but I think you can just use the linear combination fact, so first choose some $w \in V$, then
  \begin{align*}
    w &= \sum a_i v_i \\
    w &= \sum b_i u_i
  \end{align*}
  And now we can show $Tw = w$, by two steps, first
  \begin{align*}
    Tw &= \sum T(a_i v_i) \text{ and } Tw = \sum T(b_i u_i)\\
    \implies \sum (a_i - b_i)v_i = 0
  \end{align*}
  so we know that $a_i = b_i$.

  Now, we can show that
  \begin{align*}
    Tw &= \sum T(a_i v_i) \\
    &= \sum a_i u_i \\
    &= \sum b_i u_i (a_i = b_i)\\
    &= w
  \end{align*}
  so we have shown that $T = I$.
}

\bx{
  Change the basis to the eigenvectors, or any basis with an upper triangular matrix.
}

\bx{
  I think we want complex eigenvalues like $i$ twice, so $T^2$ will have $-2$ as the trace.
}

\bx{
  We have the eigenvector basis, and we know that the trace of $T^2$ is just $\sum \abs{\lambda}^2$.

  I think...I'm assuming our matrix is diagonal, although I think it's actually only upper triangular.
}

Alright, too lazy to do the rest and there's one more chapter left.